%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Solutions Architect} % Job title
    {Gol/Smiles} % Organization
    {Minas Gerais, Brazil} % Location
    {Dez. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Designed and implemented innovative technical solutions to drive growth and optimization for aviation and loyalty program platforms.
        \item Collaborated cross-functionally to align business objectives with technical architecture, ensuring scalability and performance.
        \item Evaluated emerging technologies and led platform optimization efforts to enhance efficiency and reliability.
        \item Managed risk, ensured compliance, and monitored performance metrics to optimize system performance.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Rethink} % Organization
    {Minas Gerais, Brazil} % Location
    {Nov. 2020 - Dez. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed an overall service architecture and pipelines of micro-services architecture.}
        \item {Implemented several API microservices in Node.js and in the serverless AWS Lambda functions.}
        \item {Deployed a centralized logging environment(ELK, CloudWatch, AWS X-Ray) which gather log data from lambdas and AWS resources.}
        \item {Designed the Smiles Frump, a simple nodejs lib that automatically captures unhandled errors thrown by lambda functions and formats output response based on a defined schema.}
        \item {Designed a nodejs module that mask sensitive information from given JSON (objects / arrays) using functional programming style, and pure functions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Meu Locker} % Organization
    {Minas Gerais, Brazil} % Location
    {Aug. 2018 - Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented RESTful API server for locker booking application(Meu Locker in Google Play).}
        \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, Redis, Lambda, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Brazil.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Entremetier Developer} % Job title
    {Meatballs Digital Brunch} % Organization
    {Minas Gerais, Brazil} % Location
    {Jan. 2010 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full Stack developer, building and creating awesome things, Meat-
balls is a kitchen of ideas where the ingredients are art and tech-
nology.}
        \item {Build hardware and software integrations to give live to a bunch of
experiences.}
		\item {Consulting in the development of automation systems and embed-
ded systems, microcontroller programming and development of
man-machine interface.}
		\item {Projects: Unimed Juntos Inovamos, Interactive Smell System Tools, artReality}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Analyst Developer} % Job title
    {Strata Engenharia} % Organization
    {Minas Gerais, Brazil} % Location
    {Jul. 2011 - Out. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed the AMS(Automated Maker System), an automated sys-
tem that marks the road with pre-programmed spacing (or stak-
ing) by painting the lane; with paint road marking automatically in
two colours, while the vehicle is in motion. The system is based on
a mechanical-hydraulic assembly that shoots ink on the pavement
based on the DMI.}
        \item {Implemented computing algorithms in a C\# to analyse road sur-
veys, like FWD (Falling Weight Deflectometer), IRI (International
Roughness Index), Visual Condition Surveys.}
        \item {Designed the hardware and the software from the MCSS (Multi Cam
Survey System), a vision system based on high-resolution cameras,
digital odometer (Encoder), Aided GPS (INS) and barometer. The
design has three main objectives: high resolution; high-quality im-
ages at highway speed by controlling exposure value and shutter,
precise positioning, and triggering intervals through independent
triggering channels; and various image formats at the same high
resolution.}
		\item {Designed a unified platform to get information from sensors like
GPS, INS, encoder, barometer, etc. Using a fast, secure and struc-
tured protocol.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
